peter_models

### 2024-12-13 peter_models.qmd
updating interaction terms

dataset_clean$Q271_reordered <- factor(dataset_clean$Q271,
                            levels = c("(5) Not at all important",
                                     "(4) Slightly important",
                                     "(3) Moderately important",
                                     "(2) Very important",
                                     "(1) Extremely important"))
dataset_clean$Q29_reordered <- factor(dataset_clean$Q29,
                            levels = c("(4) Not at all interested in politics",
                                     "(3) Not that interested in politics",
                                     "(2) Somewhat interested",
                                     "(1) Very interested in politics"))

@@

ord_mod_interactpoliticalID <- polr(Q29 ~ Q271_reordered * Q21 +
                               race_recoded +
                  age_recoded +
            educ +  # Educational Attainment
            S3B, # Gender
          data = dataset_clean, Hess=TRUE)

>>>>

dataset_clean$Q271_reordered <- factor(dataset_clean$Q271,
                            levels = c("(5) Not at all important",
                                     "(4) Slightly important",
                                     "(3) Moderately important",
                                     "(2) Very important",
                                     "(1) Extremely important"))
dataset_clean$Q29_reordered <- factor(dataset_clean$Q29,
                            levels = c("(4) Not at all interested in politics",
                                     "(3) Not that interested in politics",
                                     "(2) Somewhat interested",
                                     "(1) Very interested in politics"), ordered=TRUE)

@@

ord_mod_interactpoliticalID <- polr(Q29_reordered ~ Q271_reordered * Q21 +
                               race_recoded +
                  age_recoded +
            educ +  # Educational Attainment
            S3B, # Gender
          data = dataset_clean, Hess=TRUE)
